\chapter{
    Mothers' Love
}

\label{chap:TAIL-mothers-love}

The passions of the dead can be vast and mighty, but we are not all-powerful.

There are things I can never see. There are things I can never touch. There are things I can never overpower. Because of that, there are many things I can never protect my-children-who-birthed-me from. Because of that, oftentimes they die in bitterness and pain. Because of that, their deaths can also birth Hates, large and small.

Hates are things I can see and touch. I must see and touch them, because my-children-who-birthed-me cannot. I must protect my-children-who-birthed-me where I can, just as my strange brethren are driven to curse them. I do not have the power to unmake Hates. The best I can do is bind them to a seal made from things that my-children-who-birthed-me can see and touch. The truth of our nature is all we have and are, and denial of that truth is denial of our power, but, more importantly, my-children-who-birthed-me can guard themselves against what they can see and touch.

The form of a ladybird beetle or butterfly is a fine seal for small Hates. In a seal of that size, it is easy for me to reduce the power of their curses to almost nothing. The larger seals needed to hold larger Hates are more difficult. A Hate sealed as a cat can still cause sickness and misfortune.

Then there are vast Hates, birthed from wars and plagues that kill together many of my-children-who-birthed-me. There are few Loves vast enough to deny the truth of their nature, but I have tried once. It was a Hate birthed out of the smoldering rage in the hearts of so many who died knowing that their bodies would be burned together in a pit of pestilence and anonymity. I rarely call upon the power of the light that brings life to create a seal, but there was little choice against a Hate natured so strongly of death.

The weakest part of any seal is always in the eyes, because they are the windows to the soul. My-children-who-birthed-me only believe in that as a concept, but concepts are far more real to my brethren—whether they are strange or not—and I than what my-children-who-birthed-me would think of as "concrete". To line up the windows is to make an open path between a soul and the most vile curse a sealed Hate can still inflict. I used every method I knew to reinforce the seal's eyes, but even then I could not stop it from setting a cause of death in anyone it met gazes with. My blessing could only delay the curse's full effects for a single cycle around the light that brings life.

My misguided children, why did you take \hyperref[chap:SCP-023]{its} eyes?