\chapter[SCP-113 性转换器]{
    SCP-113 The Gender-Switcher\\
    SCP-113 性转换器
}

\label{chap:SCP-113}

\bb{项目编号：}SCP-113

\bb{项目等级：}Safe

\bb{特殊收容措施：}SCP-113需储存在Site-23区的标准储物柜里。把持SCP-113时应使用实验用手套。没有预先许可下，生物不可接触SCP-113。触碰到SCP-113的人员应要接受7天的医疗观察。

\bb{描述：}SCP-113的样貌像一小块红碧玉。分析显示SCP-113跟普通的碧玉的特性完全不符合。相反，SCP-113的组织较接近于{[}已编辑]。

当SCP-113与具有性染色体的生物的肉体直接接触时，生物的身体特征连带基因和肉体都会转化改变为相反性别（包括遗传性征和第二性征）。

这现象分化为四个阶段。

\bb{第一阶段：}大约持续0.2秒。SCP-113和与其接触的细胞结合，并促进一段不明化学变化。此过程导致类似烧伤的轻微伤害，且直到所有阶段完成前，SCP-113都无法从接触对象身上移除。

\bb{第二阶段：}大约持续20秒。SCP-113会发出一低能量电磁波穿透对象的身体。对象可能会感觉恶心、呕吐以及全身刺痛的感觉。

\bb{第三阶段：}大约持续60秒。在此阶段，对象的细胞构成暂时转变。变化细胞的组成范围广泛地，从无法辨认，至部分分化干细胞的独立变异。在此阶段的最后20秒，对象将感受到所有感觉神经的强烈刺激，且描述此过程极为痛苦。身体较差的对象可能会在此阶段死于休克。

此阶段结束后，对象的生物性别被永久改变。标准情况下，对象的生物性别将变为相反的生物性别。所有的第一和第二性征被相应地改变。

\bb{Stage 4:} SCP-113 disengages from the subject and becomes inert.

Subjects with sex chromosomes atypical for their species (such as intersex humans) are affected in unpredictable ways by SCP-113. In human intersex subjects, this appears to be influenced by gender identity; such subjects may be unaffected, or their bodies may change to match baseline male or female bodies (with sex chromosomes to match), or other results may occur. Usually, change seems to match or partially match subject's gender identity during initial use, if gender identity is nonstandard. Whether SCP-113 alters its effect based on the presence of a nonstandard gender identity is under investigation.

Gender identity of human subjects is not typically altered by SCP-113. In subjects with nonstandard gender identities (typically gender identities which do not match their pre-exposure biological sex), this usually results in positive psychological effects. In subjects with standard gender identities (male\slash female, matching pre-exposure biological sex), psychological effects are usually negative. These appear to be natural psychological reactions, and not an anomalous effect of SCP-113.

SCP-113 exposure results in unusual effects in certain species. In \ii{Varanus komodoensis} (the komodo dragon), a number of ZW\slash ZZ individuals were transformed to possess WW chromosomes instead of ZZ or ZW, which was in every instance fatal. In \ii{Caenorhabditis elegans} (a nematode), no males were produced despite \ii{C. elegans} having two sexes (hermaphrodite and male). Male subjects became hermaphrodites, and hermaphrodite subjects were unaffected. (Note: In wild populations, male \ii{C. elegans} are extremely rare.)

Subjects of single-sex, hermaphroditic species (such as earthworms) will not be transformed by SCP-113; the object's process will stop at the second stage and the object will become inert.

Previously exposed subjects may undergo SCP-113's effects again by re-initiating contact with SCP-113 after approximately 60 seconds have passed. However, in 25\% of cases, immediate second exposure to SCP-113 fails to transform the subject correctly. Transformation failure varies in nature, but usually includes massive bone, organ, and tissue damage to the subject, as well as partial or complete obliteration of genitalia. This commonly results in death by organ trauma or internal bleeding.

Failure rate can be affected by subjects not coming into contact with SCP-113 for a lengthy period of time, which varies by subject; patterns are under research. Under normal circumstances, transformation failure rate increases exponentially upon multiple exposures. Subjects who survive rapid, repeated exposure are eventually transformed {[}DATA EXPUNGED] Further anomalous elements continue to appear as exposure count increases.
