\chapter[SCP-128 动能效应实体]{
    SCP-128 Kinetic Energy Entity\\
    SCP-128 动能效应实体
    \footnote{由于一些原因，本文保留英文版，详见\href{https://github.com/7sDream/scp-pdf/issues/6}{Issue \# 6}}
}

\label{chap:SCP-128}

\bb{Item \#:} SCP-128

\bb{Object Class:} Euclid

\bb{Special Containment Procedures:} SCP-128 is to be held in a windowless containment chamber with blast-proof doors and walls and a ventilation system that maintains Class 100 cleanroom conditions inside. The interior of the containment chamber is to be monitored remotely by cameras welded in place with protective grating. The speakers and laser monitoring system must be similarly welded into place and protected with grating. The entry to SCP-128's containment chamber must include an antechamber with a second locked door that cannot be viewed from the chamber door.

Personnel entering the test chamber for any reason must wear ballistic armor and must not bring any loose item inside the chamber. All required equipment must be rigidly mounted to the armor. Interference with the laser monitoring system or the central wheel is forbidden unless required for maintenance.

In the center of the containment chamber, a wheel must be mounted to a concrete pedestal and allowed to spin freely. Should the wheel be measured to spin at less than 4,000 rpm at any time, all personnel are required to evacuate the containment chamber and foam nozzles will be deployed.

\tred{ARCHIVED CONTAINMENT PROCEDURES - FOR LOG PURPOSES ONLY}

\tred{FOLLOW ABOVE PROCEDURES - DO NOT ATTEMPT BELOW}

SCP-128 is to be kept in a chamber measuring at least 10 m x 10 m x 5 m with walls and door armored in 5 cm steel plate. All personnel who enter the containment room must wear full suits of heavy body armor, including ballistic plates. All loose objects \dd{of mass greater than 5 kg} are strictly prohibited. Clothing and related items are generally considered safe, as the entity appears to be incapable of distinguishing these from their wearers. Writing utensils, loose change, and other trinkets present considerable hazards to personnel and should therefore \dd{be used sparingly} never enter the containment chamber.

All items are to be cleared from room via suction before any personnel will be permitted to enter. Once personnel have exited, SCP-128 is to be given small objects, both to study its behavior and to alleviate boredom (if applicable). In the event of escape, the surrounding area will be evacuated and locked down, possibly followed by attempts to herd SCP-128 back into its enclosure. Past experience suggests that the latter is unnecessary, as the entity has shown no apparent desire to vacate the premises and will eventually return of its own accord.

\bb{Description:} SCP-128 is an immaterial source of kinetic energy which can be conferred upon any nonliving solid material within line of sight of the source. The source itself is motile, with a tendency to remain along the walls or at the central wheel of the containment chamber. The line of sight is blocked by any opaque material, including lead, steel, or even single sheets of paper, but not transparent materials such as ballistic glass. Opaque radiolucent materials will contain SCP-128's range of effect, suggesting that transmission of energy occurs at visible light wavelengths, but darkness does not prevent transmission of kinetic energy.

Any loose nonliving materials within line of sight of SCP-128 are at risk of anomalous propulsion to hazardous velocities. Items under 100 g in mass have been observed to accelerate to velocities of up to 900 m\slash s in a period of 0.1 second, similar in force to machine gun fire. Analysis of the mass and velocity of every object undergoing acceleration indicates that the system of affected objects contains a constant linear momentum of 2,500 kg m\slash s, anomalously unconstrained by direction. It is therefore advisable to have many heavier items available to the object instead of fewer, lighter items.

Despite SCP-128's invisible, immaterial form, it has been determined that the entity cannot be compressed into a space under a 2 cm radius sphere. Such compression with opaque materials, however, is not advised, as dust particles within the space will be excited, generating extreme heat, potentially rupturing the compression container explosively.

SCP-128 arbitrarily chooses which items to accelerate, with a slight statistical preference for new objects over older ones. Despite the existence of some form of acceleration choosing, tests do not indicate an active sentience directing the choice, with one exception. The object does not accelerate "living" material, with its own parameters regarding what is considered "living." People or robots moving of their own accord are not accelerated, nor is any part that is rigidly attached. Dead or unconscious people and animals are also not accelerated. Unmoving but conscious test subjects report a light "tugging" in the presence of SCP-128, which immediately stops at the first sign of movement or animal-like characteristics. Plants and fungi, alive or dead, are similarly not accelerated. Unpowered robots, however, are susceptible to acceleration.

\bb{Addendum 128-1: Recovery Log}

SCP-128 was recovered from a private home in ███████, ██. Reports of telekinesis and random anomalous kinetic activity had been previously confirmed by field agents, and MTF Mu-13 ("Ghostbusters") was called in to isolate and capture the anomaly.

\begin{scpbox}

\bb{Control:} Okay, Equipment check. Tranquilizer pistols?

\bb{Mu-13 Lead:} All pistols loaded and checked.

\bb{Control:} Ballistic armor?

\bb{Lead:} Armor check.

\bb{Mu-13 Gamma:} I'm not used to carrying this ordnance.

\bb{Control:} It's standard issue for this sort of intangible. We had to dig deep in our files, had to look up old references. SOP on this dates back to 1968. The phenomenon was called a poltergeist back then.

\bb{Delta:} Poltergeist? That is old. Type I or II?

\bb{Control:} It could be a Type I, a telekinetic vector associated with a deceased person, but field agents said that there's considerable domestic strife in the home. It's most likely undifferentiated kinetic energy from a latent Bixby under extreme stress. Type II.

\bb{Lead:} That's why containment involves the pistols. Tranq all inhabitants, and it should shut down the anomaly long enough for us to figure out whose astral it is. The standard EMP tools are for containment of an autonomous intangible, should it be Type I. Careful in there. Take no chances. Beta, get the parabolic microphone on the house. We need to identify inhabitants.

\bb{Beta:} Mike online now.

\bb{POI-1:} How many times do I have to tell you, Britney, clean your fucking room already! You're such a shitass slob!\\
\bb{POI-2:} I did! It was spotless before I went to school! It was… Oh my god, Tyler, it was you, wasn't it, you little douche!\\
\bb{POI-3:} Nuh-uh! Why would I want to step foot in your nasty-ass pigsty?

\bb{Gamma:} Considerable domestic strife, you say?

\bb{Lead:} Yeah. Just get in there and put them all to sleep. They could use the nap. And be careful with loose objects. Confirming three targets. Move out!

<Sounds of leaving the containment vehicle, approaching the house, and bashing in the door. Sound of tranquilizer pistol being fired.>

\bb{Delta:} The son's down.

\bb{Lead:} He looks young. Beta, check his vitals, make sure the drugs aren't too much of a shock to his system. The darts are calibrated to someone at least 40 kilos. Gamma, Delta, find the father and daughter now!

<Footsteps through the house. Sound of tranquilizer pistol.>

\bb{Gamma:} Father's down. Reaching for a shotgun, glad we got to him first.

\bb{Lead:} Good work, Gamma. Delta, find the daughter?

\bb{Delta:} Tracked her to her bedroom. There's stuff everywhere, here, like a tornado ripped through here. Shades are pulled. She's got a pet hamster, but I don't see her. Trying the closet.

\bb{Lead:} Careful, Delta, that's probably the source of the poltergeist activity.

\bb{Delta:} Roger that, I just got hit in the face with a pillow!

\bb{Lead:} Quick, Gamma, Delta needs backup!

<Screams heard. Sound of wood splintering. Sound of tranquilizer pistol firing.>

\bb{Delta:} Daughter is down! Repeat, Daughter is down! Chair just got thrown against the wall, bookshelf falling over! Activity increasing! Marbles! She has marbles! Ow!

\bb{Lead:} We got a Type I! Get out of the room, Delta! Dammit, just - OW! Everybody out!

\bb{Delta:} Grab my hand and pull! It's - Wait! It's the hamster! It's a fucking tornado hamster! Tranqing the hamster!

\bb{Lead:} Delta, NO! The darts aren't calibrated!

<Sound of tranquilizer pistol firing.>

\bb{Delta:} Hamster down! Why aren't you stopping! I tranqed your -

<Sound of {[}DATA EXPUNGED]>

\bb{Lead:} Everybody out! Delta down! Close the doors! Get ready for Type I containment!

\bb{<End Log>}

\bb{Closing Notes:} EMP deployment for Type I poltergeist containment functioned as expected, but failed to contain the anomaly. Mu-13 Gamma backed the MTF truck through the residence wall into the daughter's bedroom and opened the back doors. When the anomaly was observed to be inside the truck, the doors were shut and backup was called to tow the truck with accelerated debris in the armored trailer. Cover story of tornado striking the house was released.

\end{scpbox}

\bb{Addendum 128-2: Principal Researcher's Notes}

\begin{scpbox}

\bb{Principal Researcher:}\hyperref[chap:SCP-2460]{Dr. Cordelia Argent}\\
\bb{Subject:} SCP-128

Despite what the recovery log would say, this is not a poltergeist. Poltergeists are an obsolete term, anyway. This is not a spirit or a consciousness as we might think of the term. It can't pass through walls or the like. This is a source of kinetic energy. I've updated the description to show this. It's hard to say what, precisely, it is, but it appears to be best thought of as a hole through which a constant momentum enters this universe. How this is accomplished is still the subject of further tests.

In addition, the hamster did not have direct control over the phenomenon. If the hamster had conscious control, then the phenomenon would have ceased with its termination. Instead, if we continue the analogy of this being a hole, then the hamster was a valve covering the hole, which could be opened or closed to allow in more or less momentum. This "valve" appears to have been "stuck open."

So all the talk about us having the ghost of a telekinetic hamster in containment should stop. It's inaccurate.

\end{scpbox}

\tred{          scratch notes only - please delete - Dr. C. Argent}

\tred{          scratch notes only - please delete - Dr. C. Argent}

\begin{scpbox}

\bb{CArgent:} Hi \hyperref[chap:SCP-2289]{Rod}, are you there?

\bb{RodArg:} Hi Cordie, yes I am. Congrats on your promotion! How are things?

\bb{CArgent:} Okay. But I've been put in charge of 128, and its containment is stressing me out!

\bb{RodArg:} What's that? Can you send me the file?

\bb{CArgent:} Yeah, hold on.

<==sending scp128.scp==>

\bb{RodArg:} Got it. So it's some kind of kinetic energy entity? Sounds like just your sort of thing, Dr. Anomalous Physics.

\bb{CArgent:} Ha ha, very funny, bro. Yes, I've figured out it's a field of constant momentum without a center of mass. Essentially you treat the momentum of the system as a scalar constant instead of a vector, independent of direction. Simple enough, mathematically, but it does mean that the energy in the kinetic system is constantly fluctuating and being added to, to maintain the constant scalar momentum. It's supposed to be modulated up and down, but apparently it was under control of a hamster, and when the hamster died, the field got stuck at up.

\bb{RodArg:} So what's the issue about containment? There are procedures here.

\bb{CArgent:} They're ridiculous! It's basically "give it toys but take them away whenever someone enters the chamber just so it can fire the researcher's clipboard through his skull"! I've had to fill the room with foam pillows and send janitorial D-class in there in full battle armor just to clear the body away! The site director says that's not the first time, and I just…

\bb{CArgent:} What am I supposed to do?

\bb{RodArg:} You need a constant linear momentum without center-of-mass vector positioning in the containment chamber? And the controller entity of the momentum field demonstrates some familiarity with objects?

\bb{CArgent:} Yes.

\bb{RodArg:} It's a hamster. Give it a wheel.

\bb{CArgent:} It's not a ham- …That's why you're the biologist and I'm the physicist. Thank you.

\bb{RodArg:} You're still the smart one with the promotion, sis. You're welcome.

\end{scpbox}
